|

### 2023-05-11 paper/02-data.Rmd
fixed effects table
Some small edits in data section

In the forthcoming analysis, we rely on the data from the 2023 NFL Big Data Bowl provided by the NFL Next Gen Stats tracking system.
The data corresponds to 8557 passing plays across 122 games in the first eight weeks of the 2021 NFL regular season. 
For each play, we have information on the on-field location, speed, angle, direction, and orientation of each player on the field and the football at a rate of 10 Hz, along with event annotations for each frame such as ball snap, pass forward, and quarterback sack, to name a few.
For our investigation, we consider only the frames between the ball snap and when a pass forward or quarterback sack is recorded for each play.
We also remove all plays with multiple quarterbacks on the field, since we need a uniquely defined quarterback to compute our metric.
After preprocessing, there are 251,060 unique frames corresponding to moments of time from the start of the play at snap until the moment the quarterback either throws the pass or is sacked.

@@

@@

Along with the tracking information, the 2023 BDB includes scouting data provided by Pro Football Focus (PFF). 
PFF's scouting data includes manually collected player-level information at the play level, such as the player's role (e.g., whether they are a pass rusher) and credited events (e.g., player is credited with hitting the QB on the play).
In this manuscript, we use the PFF data to identify 36,362 unique players designated in the "pass rush" role across all plays.
For context, Figure \ref{fig:pass_rushers_count} displays the distribution of the number of observed pass rushers involved in a play, ranging from 1 to 8 with 4 pass rushers as the most common value.
We also leverage the PFF data to count how many hits, hurries, and sacks each pass rusher is credited with across span of collected data. 
Additionally, we use the PFF player roles to identify which players were labeled as blocking each pass rusher to adjust for opponent strength, as discussed in Section \ref{sec:methods}.

>>>>

In the forthcoming analysis, we rely on the data from the 2023 NFL Big Data Bowl provided by the NFL Next Gen Stats tracking system.
The data corresponds to 8,557 passing plays across 122 games in the first eight weeks of the 2021 NFL regular season. 
For each play, we have information on the on-field location, speed, angle, direction, and orientation of each player on the field and the football at a rate of 10 Hz, along with event annotations for each frame such as ball snap, pass forward, and quarterback sack, to name a few.
For our investigation, we consider only the frames between the ball snap and when a pass forward or quarterback sack is recorded for each play.
We also remove all plays with multiple quarterbacks on the field, since we need a uniquely defined quarterback to compute our metric.
After preprocessing, there are 251,060 unique frames corresponding to moments of time from the start of the play at snap until the moment the quarterback either throws the pass or is sacked.

@@

[^crosbysack]: A real-game footage of this play is available at https://www.raiders.com/video/de-maxx-crosby-sacks-qb-teddy-bridgewater-for-a-loss-of-6-yards-nfl

@@

Along with the tracking information, the 2023 BDB includes scouting data provided by Pro Football Focus (PFF). 
PFF's scouting data includes manually collected player-level information at the play level, such as the player's role (e.g., whether they are a pass rusher) and credited events (e.g., player is credited with hitting the QB on the play).
In this manuscript, we use the PFF data to identify 36,362 unique players designated in the "pass rush" role across all plays.
For context, Figure \ref{fig:pass_rushers_count} displays the distribution of the number of observed pass rushers involved in a play, ranging from 1 to 8 with 4 pass rushers as the most common value.
We also leverage the PFF data to count how many hits, hurries, and sacks each pass rusher is credited with across the span of observed data. 
Additionally, we use the PFF player roles to identify which players were labeled as blocking each pass rusher to adjust for opponent strength, as discussed in Section \ref{sec:methods}.
